Selective enhancement of an exploited species destabilizes ecological communities

### 2021-11-18 rmd/manuscript.Rmd
Update manuscript.Rmd

where $r_i$ is the intrinsic growth rate, $\alpha_{ij}$ the competition coefficient between species $i$ and $j$ (intraspecific competition if $i=j$; $\alpha_{ii}=1$), $K_i$ the carrying capacity, $R_t$ the number of released individuals for the enhancement of species 1, and $\epsilon_{i,t}$ the species responses to stochastic environmental fluctuations. The parameter $\phi_i$ takes a value of one when $i=1$ (otherwise zero) to represent the reproductive contribution of released individuals to the next generation of the enhanced species. The species-specific intrinsic growth rates and competition coefficients were drawn randomly from a uniform and exponential distribution, respectively, to allow for interspecific variation as $r_i \sim Unif(0.5, r_{max})$ and $\alpha_{ij, i \ne j} \sim Exp(\mu_{\alpha})$. Environmental stochasticity is random and was expressed as $\epsilon_{i,t} \sim Normal(\mu_{\epsilon}, \sigma_{\epsilon}^2)$

We varied values of `r sum(unlist(lapply(sapply(param_set, unique), length)) > 1)` parameters: $S =$ `r unique(param_set$n_species)`; $r_{max}=$ `r unique(param_set$r_max)`; $\mu_{\alpha} =$ `r unique(param_set$alpha)`; $\sigma_\epsilon =$ `r unique(param_set$sd_env)`. For simplicity, we assumed identical carrying capacities among simulated species as $K_i =$ `r unique(param_set$k)`. This setup results in `r nrow(param_set)` sets of parameter combinations that cover a range of ecological scenarios.

Under each parameter combination, we ran 1400 generations to obtain the relative temporal fluctuations (i.e., the coefficient of variation) of the whole community ($\sum_i^SN_j$), the enhanced species ($N_1$), and the unenhanced species ($\sum_{i,i \ne 1}^S N_i$). We also calculated temporal means and standard deviations for each species group.

@@

@@

>>>>

where $r_i$ is the intrinsic growth rate, $\alpha_{ij}$ the competition coefficient between species $i$ and $j$ (intraspecific competition if $i=j$; $\alpha_{ii}=1$), $K_i$ the carrying capacity, $R_t$ the number of released individuals for the enhancement of species 1, and $\epsilon_{i,t}$ the species responses to stochastic environmental fluctuations. The parameter $\phi_i$ takes a value of one when $i=1$ (otherwise zero) to represent the reproductive contribution of released individuals to the next generation of the enhanced species. The species-specific intrinsic growth rates and competition coefficients were drawn randomly from a uniform and exponential distribution, respectively, to allow for interspecific variation as $r_i \sim Unif(0.5, r_{max})$ and $\alpha_{ij, i \ne j} \sim Exp(\mu_{\alpha})$. The number of released individuals was assumed to be constant across time steps ($R_t = R$). Environmental stochasticity was drawn from a normal distribution as $\epsilon_{i,t} \sim Normal(\mu_{\epsilon}, \sigma_{\epsilon}^2)$

We varied values of four parameters: $S =$ `r unique(param_set$n_species)`; $r_{max}=$ `r unique(param_set$r_max)`; $\mu_{\alpha} =$ `r unique(param_set$alpha)`; $\sigma_\epsilon =$ `r unique(param_set$sd_env)`. For simplicity, we assumed identical carrying capacities among simulated species as $K_i =$ `r unique(param_set$k)`. This setup resulted in `r nrow(param_set)` sets of parameter combinations that cover a range of ecological scenarios.

Under each parameter combination, we ran 1400 time steps of 1000 independent communities (i.e., simulation replicates) with the gradient of the number of released individuals $R$ (0 - 500). We initialized the community with populations of each species drawn from a poisson distribution with a mean of five. We repeated the seeding procedure every 10 time steps over the first 200 time steps to allow species to establish populations and reach an equilibrium without (initialization period). After the initialization period, we released $R$ individuals of the enhanced species every time step over the next 200 time steps to reach a new equilibrium with selective enhancement (burn-in period). We saved the last 1000 time steps to obtain the relative temporal fluctuations (i.e., the coefficient of variation) of the whole community ($\sum_i^SN_j$), the enhanced species ($N_1$), and the unenhanced species ($\sum_{i,i \ne 1}^S N_i$). We also calculated temporal means and standard deviations for each species group. Values of simulation parameters were summarized in XXX. We performed simulations using R version XXX.

@@

**Time-series data of fish abundance.** We assembled time-series data across XX sites within XX protected watersheds of Hokkaido Island, Japan. At these sites, long-term monitoring of fish abundance began in 1971 but effective sampling methods (a combination of electrofishing and cast net sampling) were implemented in 1999. Data were collected in summer to fall with irregular sampling intervals (0 to 3 year intervals for most cases). After careful data selection (Supporting Information), we used time-series data of fish abundance at XX sites during a period of 1999-2019.

**Fish stocking data of masu salmon.** Ask Urabe to write this part

**Environmental data.** At each sampling site,we collected the following data as potential covariates: upstream watershed area (km^2^; a proxy for stream size), proportional land use in the upstream watershed (forest, agriculture, urban), local species richness, local climates (annual mean air temperature [unit] and cumulative precipitation [mm]), and ocean productivity (Chlorophyll a [unit]).

@@

We quantified the coefficient of variation (CV), temporal mean ($\mu$) and standard deviation ($\sigma$) of these local fish communities through the following procedure.
